### 2020-09-20 Thesis-Chapter3-Arguments.tex
Update Ch3 outline and add CSAM sources

@@

% - But we're _exactly_ following the classical analytic method! Well, yes, but in a cooperative manner, knowing it will
%     require iteration, and being careful about side effects. It's an agile approach to policy making, but it's still
%     policy making.

@@

rozenshtein_wicked_2018:
- Approaches
  - Muddling through (he cites Charles E. Lindblom, just like feeley_judicial_2000!)
  - Risk management (--finally, something familiar to security experts!)
    - So, a broader view of security, inclusive of both public safety and information security
    - In this model, threat actors now include terrorists, CSAM distributors, organized crime
    - I have already suggested adding government mandates to the traditional IS threat model
  - Imperfect solutions, like lawful hacking
  - Meanwhile, invest in knowledge production and improved relationships (like "cross-organizational" from
      commission_tackling_2018)
- Avoid
  - Easy answers ("narrow solutions" from commission_tackling_2018)
    - Such as EA mandates or "golden age of surveillance"-based denials

@@

%%%%%%%%%%%%
% Chapter 4, threat models
% (how to be specific enough to be useful but generic enough to apply to many systems? Focus on the EA type (DAR v DIM),
%   then apply to specific systems)
% DAR, DIM threat models (make sure to cover abelson_2015)
% Basic proposals
%  --> mappings onto threat models
% At work: 3 example systems analyzed with this threat model
% 1. IM (E2E IM too?) -- in motion
% 2. Cloud storage -- at rest
% 3. Mobile phone -- at rest, but way different scenario than cloud
%  --> include Ozzie's CLEAR, since it was higher profile
%%%%%%%%%%%%

% Leave for conclusion chapter:
% Subject four: now what?
%  --> How current proposals stack up against desired properties, threat model
%  --> security expert? do research, provide clear security advice, be vigilant
%  --> policymaker? fund research, don't mislead, don't be premature
%  --> either? know that there is no stable solution, balance rules and principles, serve your neighbor
% see varia_2018

@@

The debate over exceptional access takes place on two fundamental levels:
\begin{enumerate}
    \item Whether cryptosystems with exceptional access represent a net benefit to society
    \item Whether and how to conduct exceptional access research
\end{enumerate}

\subsection{Arguments For}

Why EA is a benefit to society:
\begin{itemize}
    \item Absolute privacy is not a right
    \item Encryption gives too much power to the individual
    \item EA would allow more crimes to be prevented and prosecuted
\end{itemize}

Why to research EA:
\begin{itemize}
    \item EA done well would be more secure and privacy preserving than EA done poorly
    \item The threat of legislative action creates urgency
\end{itemize}

\subsection{Arguments Against}

Why EA is a danger to society:
\begin{itemize}
    \item Privacy is an absolute right
    \item Exceptional access gives too much power to the state
    \item Exceptional access is not possible in an acceptably secure manner
\end{itemize}

Why not to research EA:
\begin{itemize}
    \item With both security and privacy in a poor state, research should be focused on strengthening, not weakening,
            them
    \item The technical community should not entertain delusions about what is truly possible
\end{itemize}

\subsection{Fallacious Arguments}

Fallacy definitions come from the helpful University of North Carolina Writing Center \cite{unc_2020}. Also cited:
\cite{hanna_2019}.

Fallacies are as shown in \myfig{fig-args-fallacies}.

\begin{figure}[h]
    \centering\CaptionFontSize
    \myincludeargument{comprehensive.fallacies}
    \caption[Fallacious Arguments]{Fallacious arguments used in the exceptional access debate.}
    \label{fig-args-fallacies}
\end{figure}

>>>>

\subsection{Plan for this Chapter}

% - But we're _exactly_ following the classical analytic method! Well, yes, but in a cooperative manner, knowing it will
%     require iteration, and being careful about side effects. It's an agile approach to policy making, but it's still
%     policy making.
% Already covered defining the problem. Next will discuss goals and list alternatives. That will feed into threat
% modeling.

@@

@@

rozenshtein_wicked_2018:
- Approaches
  - Muddling through (he cites Charles E. Lindblom, just like feeley_judicial_2000!)
  - Risk management (--finally, something familiar to security experts!)
    - So, a broader view of security, inclusive of both public safety and information security
    - In this model, threat actors now include terrorists, CSAM distributors, organized crime
      - Add a new character? Evil Alice and evil Bob (Alex and Becca?)? This automatically raises to question of how to
          identify bad actors--AI (lee_detecting_2020)? PhotoDNA (microsoft_2020)? Government orders (warrants)? Could
          be useful.
    - I have already suggested adding government mandates to the traditional IS threat model
  - Imperfect solutions, like lawful hacking
  - Meanwhile, invest in knowledge production and improved relationships (like "cross-organizational" from
      commission_tackling_2018)
- Avoid
  - Easy answers ("narrow solutions" from commission_tackling_2018)
    - Such as EA mandates or "golden age of surveillance"-based denials

@@

@@

% The debate over exceptional access takes place on two fundamental levels:
% \begin{enumerate}
%     \item Whether cryptosystems with exceptional access represent a net benefit to society
%     \item Whether and how to conduct exceptional access research
% \end{enumerate}

% \subsection{Arguments For}

% Why EA is a benefit to society:
% \begin{itemize}
%     \item Absolute privacy is not a right
%     \item Encryption gives too much power to the individual
%     \item EA would allow more crimes to be prevented and prosecuted
% \end{itemize}

% Why to research EA:
% \begin{itemize}
%     \item EA done well would be more secure and privacy preserving than EA done poorly
%     \item The threat of legislative action creates urgency
% \end{itemize}

% \subsection{Arguments Against}

% Why EA is a danger to society:
% \begin{itemize}
%     \item Privacy is an absolute right
%     \item Exceptional access gives too much power to the state
%     \item Exceptional access is not possible in an acceptably secure manner
% \end{itemize}

% Why not to research EA:
% \begin{itemize}
%     \item With both security and privacy in a poor state, research should be focused on strengthening, not weakening,
%             them
%     \item The technical community should not entertain delusions about what is truly possible
% \end{itemize}

% \subsection{Fallacious Arguments}

% Fallacy definitions come from the helpful University of North Carolina Writing Center \cite{unc_2020}. Also cited:
% \cite{hanna_2019}.

% Fallacies are as shown in \myfig{fig-args-fallacies}.

% \begin{figure}[h]
%     \centering\CaptionFontSize
%     \myincludeargument{comprehensive.fallacies}
%     \caption[Fallacious Arguments]{Fallacious arguments used in the exceptional access debate.}
%     \label{fig-args-fallacies}
% \end{figure}
